---
title: "Google Finance API"
author: "Pedro Moreira"
date: "14 August 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("GoogleFinanceAPI.R")
```

## Get stock price
The google finance API is accessible in multiple ways. One option is to use an API hosted at finance.google.com

# finance.google.com

For example the following URL <http://finance.google.com/finance/info?client=ig&q=NASDAQ%3AAAPL,GOOG> retrieves the price of Apple and Google.

q takes the form of Excahnge:Symbols, where Symbols is a comma separate list of stock symbols (e.g. NASDAQ:AAPL,GOOG).

The data returned contains several attributes, such as:
Attribute | Description
----------| -------------
  id	    | ID
  t       | StockSymbol
  e       | Index
  l       | LastTradePrice
  l_cur	  | LastTradeWithCurrency
ltt	      | LastTradeTime
lt_dts	  | LastTradeDateTime
  lt	    | LastTradeDateTimeLong
  div	    | Dividend
  yld	    | Yield
  s	      | LastTradeSize
  c	      | Change
  cp	    | ChangePercent
  el	    | ExtraHrsLastTradePrice
  el_cur	| ExtraHrsLastTradeWithCurrency
  elt	    | ExtraHrsLastTradeDateTimeLong
  ec	    | ExtraHrsChange
  ecp	    | ExtraHrsChangePercent
  pcls_fix| PreviousClosePrice



```{r }
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
